 
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[usenames,dvipsnames,table]{xcolor}
%this line in for table colors
\usepackage{sectsty}


\usepackage{tabto}    
\newcommand\mytab{\tab \hspace{-8cm}}

\definecolor{sgray}{gray}{0.3}

\usepackage{titlesec}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
colorlinks = true,
%linkcolor = blue, 
%urlcolor  = blue,
%citecolor = blue,
%anchorcolor = red,
allcolors=blue,
]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-4.0pt}

%this sets space between multicol list
\setlength{\columnsep}{-6pt}%\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% accepted
%\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%custom 
\setlist[itemize,1]{label=$\diamond$}
\setlist[itemize,2]{label=$\diamond$}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section }{ 
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{sgray}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \textcolor{sgray} {\textit{\small#3}} & \textcolor{sgray}{ \textit{\small #4} }\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSmall}[4]{
	\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r} 
	$\diamond$ \hspace{1mm}	#1 (#2) & #4 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingD}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \textcolor{sgray} {\textit{\small#3}} & \textcolor{sgray}{ \textit{\small #4} }\\
    \end{tabular*} %\vspace{10pt}\\
    \\ \vspace{3pt}
    Description:{#5}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% todo: telegram bots and google drive is missing 
%todo  # I think It's better to move it to a new project 




%todo genetic algorithm for AI
%todo git EN-FA-CS-Dictionary


% delete information from github and add it to site

%todo stimulsoft report
\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge 
    %\scshape
     Amir Pourmand} \\ \vspace{5pt}
   \textcolor{sgray}{\small Department of Computer Engineering, Sharif University of Technology, Azadi Avenue, Tehran, Iran, 11155-11365} \\ \vspace{2pt}
   
  
   
 % \small \raisebox{-0.1\height}\faPhone\  (+98)-913-002-7522 
    ~ 
 \href{mailto:pourmand1376@gmail.com}{ 
 	\textcolor{black}{
 	\raisebox{-0.2\height}\faEnvelope\  pourmand1376@gmail.com}}
~ 
 \href{mailto:a.pourmand@sharif.edu}
 {
 	\textcolor{black}{
 	\raisebox{-0.2\height}\faEnvelope\  a.pourmand@sharif.edu}}
\vspace{3pt}
 ~ 
    \href{https://linkedin.com/in/amir-pourmand/}
    { \textcolor{black}{
\raisebox{-0.2\height}
    \faLinkedin\ linkedin.com/in/amir-pourmand}}
    ~
    
    
    \href{https://github.com/pourmand1376}{\textcolor{black}{
    \raisebox{-0.2\height}
    \faGithub\ github.com/pourmand1376}}
    \vspace{-8pt}
    ~ 
    \href{https://amirpourmand.ir/}{
    	\textcolor{black}{
    	\raisebox{-0.2\height}\faGlobe\ https://amirpourmand.ir/}}
    ~ \href{https://aprd.ir/}{
    	\textcolor{black}{
    		\raisebox{-0.2\height}\faGlobe\ https://aprd.ir/}}
    
    \vspace{-8pt}
\end{center}

\vspace{1pt}


%------------Research Interest---------
\section{Research Interests}
\begin{multicols}{4}
            \begin{itemize}[
            	%itemsep=-2pt, parsep=4pt
            	]
           % 	\noindent
	           \item Deep Learning
	           \item Computer Vision 
	           \item NLP
	           \item Interpretability
            \end{itemize}
        \end{multicols}
        \vspace*{1.0\multicolsep}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Sep. 2020 - Present}
      {Master of Science in Artificial Intelligence and Robotics}{Tehran, Iran}
  \resumeSubHeadingListEnd
    

\begin{itemize}[itemsep=-3pt, parsep=5pt]
\item  GPA: \textbf{18.83/20} or 4/4

\item Relevant courses:
Deep Learning (19.4/20),
Natural Language Processing (19.4/20), \\
Machine Learning (19.5/20),
Statistical Machine Learning (19/20), 

\item Master's Project (Supervisor:  \hyperref[references]{Prof. Hamid R. Rabiee}):
\vspace*{-0.2cm}
\begin{itemize}[itemsep=-3pt, parsep=5pt]
\item Project Title: Real-time automatic Polyp detection and classification using interpretable AI (XAI)

\item Project Summary: 
The purpose of this paper is to enhance the YOLO algorithm's performance in handling labeled and unlabeled data using a semi-supervised learning framework. The study proposes an innovative approach that integrates semi-supervised learning and interpretability to improve the performance and transparency of the YOLO algorithm.
%todo better project summary
\end{itemize}
\end{itemize}  


  \resumeSubHeadingListStart
    \resumeSubheading
      {Yazd University}{Sep. 2016 - Sep. 2020}
      {Bachelor of Science in Computer Engineering}{Yazd, Iran}
  \resumeSubHeadingListEnd
  
\begin{itemize}[itemsep=-3pt, parsep=5pt,label={$\diamond$}]

\item GPA: \textbf{17.47/20} or 3.66/4 , Units: 140


\item  Relevant courses (GPA: \textbf{19.95/20}):
Intelligence and Expert systems (19.7/20),
Foundations of Information Retrieval and Web Search (20/20),
Fundamentals of Information Technology (20/20),
Microprocessors and Assembly Language (20/20),
Principles of Database Design (20/20),
Internet Engineering (20/20)

\item Bachelor's Project (Supervisor: \hyperref[references]{Prof. V. Derhami} ):
\vspace*{-0.2cm}
\begin{itemize}[itemsep=-3pt, parsep=5pt]
\item Project Title: 
A Recommendation System for shopping centers using Apriori Algorithm

\item Project Summary: 
We analyzed data from an SQL-Server database to find frequent item sets and compute metrics such as lift. These insights were then used to suggest products to customers.
\end{itemize}



\end{itemize}  
  
\begin{comment}
\resumeSubHeadingListStart
    \resumeSubheading
      {Malek Sabet High School}{Sep 2012 - June. 2016}
      {Diploma in Physics and Mathematics Discipline}{Yazd, Iran}
  \resumeSubHeadingListEnd
 \small{ GPA: \textbf{19.49}/20, Units: 102, {\href{https://en.wikipedia.org/wiki/Governmental_leading_high_school}{ Affiliation: Governmental leading high school}}
\end{comment}  

\section{Honors and Awards}
\begin{itemize}



\item Ranked \textbf{\large 1st} among over 16,000 graduate applicants in the Iranian National University Entrance Exam (Konkur) for M.Sc. of Computer Engineering \textbf{in 7 (all CE) majors}, August 2020 (This rank is \textbf{unprecedented} in history of CE University entrance exam). 


\item \textbf{Silver Medal} in the 25th Scientific Olympiads for Iranian University Students in February 2021. 
\item Awarded a grant by National Elite Foundation for two semesters (1 year), October 2021.

\item Ranked 1st in the 24th Scientific Olympiads for Iranian University Students in Region 6 and Ranked 16th in the country in 2019. 
 
 
 \item Offered admission to M.Sc. program in Artificial Intelligence at Yazd
University as a talented undergraduate student, August 2020. 
%(This special position is offered to few B.Sc. students with highest GPAs to be straightly admitted to M.Sc. program). 

\item Ranked among the top 1 percent in the Iranian National University Entrance Exam
(1896th among over 300,000 participants), June 2016. 

%TOP 9 in yazd

\end{itemize}

\section{Under-Preparation Papers}
\resumeSubHeadingListStart
\resumeSubheadingD
{Semi-Supervised Polyp Detection and Classification via Interpretable AI}{Jun 2021 - Present}
{Sharif University of Technology, Tehran University of Medical Sciences }{
	Supervisor: Prof. Hamid R. Rabiee}
{ 
	We are writing this paper alongside my master thesis. 
}

\section{To Be Submitted Papers}
\resumeSubHeadingListStart
\resumeSubheadingD
{Real-time Detection of  Brain Aneurysm via Multi-View YOLOv5}{Jun 2022 - Present}
{Sharif University of Technology, Tehran University of Medical Sciences }{
Supervisor: Prof. Hamid R. Rabiee}
{ %
Our project involved customizing the YOLOv5 algorithm to detect brain aneurysms in 2.5D CT scans. The network structure was modified to accept multiple images of the same patient as a single input, which helped the network to make better use of available information.
}
%todo edit unpublished works with Dr.Taheri
\resumeSubHeadingListEnd


%todo edit unpublished works with Dr.Taheri
\resumeSubHeadingListEnd

\section{Academic Projects}

\resumeSubHeadingListStart
\resumeSubheading
{Deep Learning}{Aug 2021 - Jan 2022}
{Sharif University of Technology, \url{https://github.com/pourmand1376/DL-Homeworks}}{Supervisor: Prof. Hamid Beigy}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Stochastic Process}{Aug 2021 - Jan 2022}
{Sharif University of Technology, \url{https://github.com/pourmand1376/SP-Homeworks}}{Supervisor: Prof. Hamid R. Rabiee}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Machine Learning}{Jan 2021 - July 2021}
{Sharif University of Technology, \url{https://github.com/pourmand1376/ML-projects}}{Supervisor: Dr. M. Rohban}

\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Statistical Machine Learning}{Jan 2021 - July 2021}
{Sharif University of Technology, \url{https://github.com/pourmand1376/SML-projects}}{Supervisor: Prof. Rabiee}

\resumeSubHeadingListEnd


\resumeSubHeadingListStart
\resumeSubheading
{Digital Image Processing}{Jan 2021 - July 2021}
{Sharif University of Technology, \url{https://github.com/pourmand1376/DIP-projects}}{Supervisor: Prof. Kasaei}

\resumeSubHeadingListEnd



\resumeSubHeadingListStart
    \resumeSubheading
      {Compiler and Parser}{December 2019}
      {Yazd University, \url{https://github.com/pourmand1376/Parser}}{Supervisor: Dr. ZarePour}
      { 
      	%Implementation of LL(0), LR(0), SLR(1), CLR(1) algorithms in C\# from scratch.
       }
 \resumeSubHeadingListEnd


\resumeSubHeadingListStart
    \resumeSubheading
      {Web Crawler, Indexer and Search Engine Web Application}{November 2018}
      {Yazd University, \url{https://github.com/pourmand1376/Crawler}}{Supervisor: Dr. A. Zareh}
      { %Web Crawler fetches all sites from the seeds and crawls all other related links. The indexer prepares the data for immediate search from the search engine web application. 
      }  
 \resumeSubHeadingListEnd
 
 
 % todo: Add ML (help afhsin)
 % todo: ADD SML
 % todo: add Image processing
 % todo : add AI-Project in derhami class
 
\section{Industrial Projects}

%todo sort by time
\resumeSubHeadingListStart
\resumeSubheadingD
{Heart Rate Monitor Application (ECG)}{
	July 2019 - Sep 2019
 }
{Yazd University}
{Supervisor: Prof. V. Derhami}
{The app receives real-time data from a wireless ECG device via Bluetooth and displays it as a graph. However, some of the data was distorted or lost, making it difficult to consistently display it. }
\resumeSubHeadingListEnd


  \resumeSubHeadingListStart
    \resumeSubheadingD
      {Web application to manage invoice and account }{January 2019 – March 2019}
      {Amapardazesh Sepand Inc., Tavoni Etebar Kargaran Bafgh (Samen)}{Supervisor: S. Tavakoli}
      {
      	This web application provides a RESTful API for Android clients and an ASP.NET web application to show customers how much they owe the company.}
  \resumeSubHeadingListEnd
  
  
 
  
  \resumeSubHeadingListStart
  \resumeSubheadingD
  {Car Management for IranKhodro}{July 2013 – November 2013}
  {Amapardazesh Sepand Inc., IranKhodro Yazd (4022 Branch - Farashahi)}{Supervisor: S. Tavakoli}
  { My first encounter with any programming language was with this Windows-forms application that managed parking lots, controlled vehicle entrance and exit, and generated management reports. }
  \resumeSubHeadingListEnd
  
  
  
  
  \section{Open Source Contributions}
  
   \resumeSubHeadingListStart
  \resumeSubheading
  {Contributions to YOLOv5}{2022}
  {Link to repo: \url{https://github.com/ultralytics/yolov5},
\href{https://github.com/ultralytics/yolov5/issues/9059}{\#9059},
\href{https://github.com/ultralytics/yolov5/pull/8694}{\#8694},
\href{https://github.com/ultralytics/yolov5/pull/8766}{\#8766}  
 }{Maintainer: Glenn Jocher}{ 
  %	I have solved a very important bug and I have some PRs
}
  \resumeSubHeadingListEnd
   \resumeSubHeadingListStart
  \resumeSubheading
  {Contributions to al-folio}{June 2022}
  {Link to repo: \url{https://github.com/alshedivat/al-folio} }{Maintainer: Al-Shedivat}{
  	
}
  \resumeSubHeadingListEnd
  
    \resumeSubHeadingListStart
  \resumeSubheading
  {Open source Crawler for Persian websites}{July 2022}
  {Link to repo: \url{https://github.com/pourmand1376/PersianCrawler} }{Maintainer: Me}
  \resumeSubHeadingListEnd
  
  
   \resumeSubHeadingListStart
  \resumeSubheading
  {Translating ShareX to Persian (\href{https://github.com/ShareX/ShareX/pulls?q=Persian}{Link})}{July 2019 – August 2019}
  {Link to repo: \url{https://github.com/ShareX/ShareX} }{Maintainer: Jaex}
  \resumeSubHeadingListEnd
  
  
\section{Internships}

\resumeSubHeadingListStart
    \resumeSubheadingD
      {Web application for restaurant }{July 2018 – October 2018}
      {Amapardazesh Sepand Inc. }{Supervisor: S. Tavakoli}
      {
 As well as developing a RESTful API service for Android devices, I built a dashboard  (based on ASP.NET) for managers to customize the restaurant according to their preferences.
  }
  \resumeSubHeadingListEnd

\section{Teaching Experiences}

\resumeSubHeadingListStart
\resumeSubheadingSmall
{Statistical Machine Learning}{ Feb 2023 - Present }
{Sharif University of Technology} {Supervisor: Dr. Hamid R. Rabiee}
%{ Desiging and grading of Homework \#1 and \#3}
\resumeSubHeadingListEnd   

\resumeSubHeadingListStart
\resumeSubheadingSmall
{Deep Learning}{ Aug 2022 - Present }
{Sharif University of Technology} {Supervisor: Dr. Hamid Beigy}
%{ Desiging and grading of Homework \#1 and \#3}
\resumeSubHeadingListEnd   

\resumeSubHeadingListStart
\resumeSubheadingSmall
{Linear Algebra}{ Aug 2022 - Present }
{Sharif University of Technology} {Supervisor: Prof. Hamid R. Rabiee}
%{ Desiging and grading of Homework \#1 and \#3}
\resumeSubHeadingListEnd   

\resumeSubHeadingListStart
\resumeSubheadingSmall
{Stochastic Processes for Bioinformatics}{ Jan 2022 - July 2022 }
{Sharif University of Technology} {Supervisor: Dr. Mohammad H. Rohban}
%{ Desiging and grading of Homework \#1 and \#3}
\resumeSubHeadingListEnd   

\resumeSubHeadingListStart
\resumeSubheadingSmall
%todo here should be written more precisely
{Linear Algebra }{Aug 2021 - Jan 2022}
{Sharif University of Techonlogy}{Supervisor: Prof. Hamid R. Rabiee}
%{ Designing and grading of Practical homework \#5 }
\resumeSubHeadingListEnd   
\resumeSubHeadingListStart
\resumeSubheadingSmall
%todo here should be written more precisely
{Operating Systems Laboratory }{Aug 2021 - Jan 2022}
{Sharif University of Technology, \url{https://github.com/Sharif-OS-Lab}}{Supervisor: Dr. Beigy}
\resumeSubHeadingListEnd   

\resumeSubHeadingListStart
    \resumeSubheadingSmall
      {Principles of IT Strategic Management \& Planning }{January 2019 – July 2019}
      {Yazd University}{Supervisor: Dr. M. Matinkhah}
  \resumeSubHeadingListEnd   
   
  \resumeSubHeadingListStart
   \resumeSubheadingSmall
      {Fundamentals of Information Technology }{September 2018 – January 2019}
      {Yazd University}{Supervisor: Dr. M. Matinkhah}
%      { Designing and grading of homework, Updating course website}
  \resumeSubHeadingListEnd      
      
      
      
  \resumeSubHeadingListStart
    \resumeSubheadingSmall
      {Programming Fundamentals }{January 2018 –July 2018}
      {Yazd University}{Supervisor: Dr. R. SheykhPour}
%      { Teaching once a week
 %     	%todo رفع اشکال 
  %    	, Grading exams, Designing and grading of homework}

  \resumeSubHeadingListEnd      
      
\section{Work Experiences}


\resumeSubHeadingListStart
    \resumeSubheadingD
      {Software Developer }{July 2016 – January 2020}
      {Amapardazesh Sepand Inc. }{Supervisor: S. Tavakoli}
      { The projects I worked on during my four years with Sepand Inc. were as follows: }
      
      %todo sepand projects
      \resumeItemListStart
      \resumeItem{Query Optimization in SQL-Server}
      \resumeItem{Automatic updating of application using GoogleDrive API}
      \resumeItem{ Report generator for DataGridView in StimulSoft Report }
      \resumeItem{Integrating different devices (POS, Scale, SMS, TelegramBot) with Sepand Application}
      \resumeItem{Database Schema Comparer and Upgrader using DACPAC}
      \resumeItemListEnd 
      
  \resumeSubHeadingListEnd


\resumeSubHeadingListStart
    \resumeSubheadingD
      {English Teacher }{July 2017 – January 2018}
      {Zaban Gostar Institute  }{Supervisor: F. Fatemi}
      { For a period of one term, I was an English instructor at Zaban Gostar Institute.
      }
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, 
 label={}
 ]
    \small{\item{
     \textbf{Programming Languages}{: Proficient: Python, C\#, SQL (T-SQL); Intermediate: Java, MATLAB } \\
     \textbf{Developer Tools}{: VIM ,VS Code, Jupyter Notebooks, Visual Studio, Android Studio} \\
     %\textbf{Technologies/Frameworks}{: ASP.NET MVC, Jekyll } \\
     \textbf{Databases}{: Proficient in SQL-Server, Familiarity with Mongo-Db } \\
     \textbf{Tools}{: \LaTeX , Git, Docker, Jekyll } \\
     \textbf{Operating Systems}{: Manjaro  (Arch Linux), Kubuntu  (Debian), Fedora (KDE spin), Windows } \\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Languages}
 \begin{itemize}[leftmargin=0.15in, 
 label={}
 ]
    \small{\item{
    		%todo this should be in certificate section
     \textbf{English}{:\mytab \href{https://amirpourmand.ir/pdf/toefl.pdf}{TOEFL}: 103 (R: 27, L: 26, S:24, W:26) 
      (Equivalent to C1) \\ \hspace{1.4cm} 
     \mytab	\href{https://amirpourmand.ir/img/ili.jpg}
     	{ILI Certificate} (Equivalent to C2)} \\
  \textbf{Persian}{:\mytab Native}\\
  \textbf{Arabic}{:\mytab Basic}
     }}
\end{itemize}


%todo To save space I will place all my certificates in linkedin account

%-----------INVOLVEMENT---------------
\section{Extracurricular}
   %chess ! swimming % hiking
 \begin{itemize}[leftmargin=0.15in, 
	label={}
	]
	\small{\item{
			\textbf{Sports}{: Mountain climbing, biking, swimming, playing chess!} \\
			\textbf{Other activities}
			{: Blogging (see 
				\href{https://amirpourmand.ir/blog}
				{amirpourmand.ir/blog} and 
				\href{https://aprd.ir}{aprd.ir}}
				)}\\
	}
\end{itemize}
\section{References}
\label{references}
\resumeSubHeadingListStart
    \resumeSubheading
      {Prof. Hamid R. Rabiee}{\href{mailto:rabiee@sharif.edu}{rabiee@sharif.edu} }{Professor of Computer Engineering Department,
\url{http://sharif.edu/~rabiee/}}{Sharif University of Technology}
 \resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Prof. Vali Derhami}
      {\href{mailto:vderhami@yazd.ac.ir}{vderhami@yazd.ac.ir}}
      {Professor of Computer Engineering Department,
\url{https://pws.yazd.ac.ir/derhami/en/}}{Yazd University}
 \resumeSubHeadingListEnd
 
% \resumeSubHeadingListStart
%    \resumeSubheading
%      {Dr. Mojtaba Matinkhah}
%      {\href{mailto:matinkhah@yazd.ac.ir}{matinkhah@yazd.ac.ir}}
%      {Assistant professor of Computer Engineering Department, 
%\url{https://pws.yazd.ac.ir/matinkhah/}}{Yazd University}
% \resumeSubHeadingListEnd
 
%  \resumeSubHeadingListStart
%    \resumeSubheading
%      {Dr. Jamal ZarePour}
%      {\href{mailto:zarepourjamal@yazd.ac.ir}{zarepourjamal@yazd.ac.ir}}
%      {Assistant professor of Computer Science Department,
%\url{https://pws.yazd.ac.ir/jzarepour/}}{Yazd University}
% \resumeSubHeadingListEnd


\end{document}




\begin{comment}
list of things in my linkedin which are deleted

Update Sepand with google drive
Google Drive Api for upgrading appliction
work with google drive API's to upgrade existing application files such as DLL's, reports and so on.  This was replacement for Microsoft Click Once Deployment customized for our business.
The app is written with c# in a WPF application.

!this one has github link! 
Telegram bot for group manangement
Using telegram bot documentation from api.telegram.org, I've written a bot for managing groups in telegram. It can detect URL's, turn the group off at night, filter messages, delete inapropriate content and etc.

Comparing and Updating SQL Server database
I've written an application for updating customer local SQL Server databases through Sqlpackage which uses DAC framework.
This way we can compare two databases and generate script for updating schema in about 2 minutes. It also works with google drive api to download .dacpac file.

Report generator for Stimulsoft report
\end{comment}


\begin{comment}
\resumeSubHeadingListStart
\resumeSubheading
{Integrating different devices and technologies with Sepand software }{July 2016 – January 2020}
{Amapardazesh Sepand Inc.}{Supervisor: S. Tavakoli}

\resumeItemListStart
\resumeItem{Scale: Radin, MahakScale, Sadr, TarazSystem, Azma}
\resumeItem{POS: IranKish, SamanKish, IranKish, TejaratPardakht, MabnaKartArya}
\resumeItem{SMS: NegarSMS, Tooba, SMSNiaz}
\resumeItem{CallerId: ManshooreSimin}
\resumeItem{TelegramBots: Manager Reports Bot, Group Manager Bot}
\resumeItem{GoogleDrive: Updating sepand accounting software with files hosted on google drive automatically}
\resumeItemListEnd 
\resumeSubHeadingListEnd  
%todo this should be included in sepand desc



\resumeSubHeadingListStart
\resumeSubheadingD
{Database Schema Comparer and Upgrader}{April 2019 – May  2019}
{Amapardazesh Sepand Inc.}{Supervisor: S. Tavakoli}
{ Compare two SQL-server databases and update the schema of the database to newer version }
\resumeSubHeadingListEnd

\end{comment}
