 
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% use XeLATEX to compile
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[usenames,dvipsnames,table]{xcolor}
%this line in for table colors
\usepackage{sectsty}


\usepackage{tabto}    
\newcommand\mytab{\tab \hspace{-8cm}}

\definecolor{sgray}{gray}{0.3}

\usepackage{titlesec}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
colorlinks = true,
%linkcolor = blue, 
%urlcolor  = blue,
%citecolor = blue,
%anchorcolor = red,
allcolors=blue,
]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-4.0pt}

%this sets space between multicol list
\setlength{\columnsep}{-6pt}%\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% accepted
%\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%custom 
\setlist[itemize,1]{label=$\diamond$}
\setlist[itemize,2]{label=$\diamond$}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section }{ 
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{sgray}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \textcolor{sgray} {\textit{\small#3}} & \textcolor{sgray}{ \textit{\small #4} }\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSmall}[4]{
	\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r} 
	$\diamond$ \hspace{1mm}	#1 (#2) & #4 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingD}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \textcolor{sgray} {\textit{\small#3}} & \textcolor{sgray}{ \textit{\small #4} }\\
    \end{tabular*} %\vspace{10pt}\\
    \\ \vspace{3pt}
    Description:{#5}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% todo: telegram bots and google drive is missing 
%todo  # I think It's better to move it to a new project 




%todo genetic algorithm for AI
%todo git EN-FA-CS-Dictionary


% delete information from github and add it to site

%todo stimulsoft report
\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge 
    %\scshape
     Amir Pourmand} \\ \vspace{5pt}

   
  
   
 % \small \raisebox{-0.1\height}\faPhone\  (+98)-913-002-7522 
    ~ 
 \href{mailto:pourmand1376@gmail.com}{ 
 	\textcolor{black}{
 	\raisebox{-0.2\height}\faEnvelope\  pourmand1376@gmail.com}}
~ 
 \href{mailto:a.pourmand@sharif.edu}
 {
 	\textcolor{black}{
 	\raisebox{-0.2\height}\faEnvelope\  a.pourmand@sharif.edu}}
\vspace{3pt}
 ~ 
    \href{https://linkedin.com/in/amir-pourmand/}
    { \textcolor{black}{
\raisebox{-0.2\height}
    \faLinkedin\ linkedin.com/in/amir-pourmand}}
    ~
    
    
    \href{https://github.com/pourmand1376}{\textcolor{black}{
    \raisebox{-0.2\height}
    \faGithub\ github.com/pourmand1376}}
    \vspace{-8pt}
    ~ 
    \href{https://amirpourmand.ir/}{
    	\textcolor{black}{
    	\raisebox{-0.2\height}\faGlobe\ https://amirpourmand.ir/}}
    ~ \href{https://aprd.ir/}{
    	\textcolor{black}{
    		\raisebox{-0.2\height}\faGlobe\ https://aprd.ir/}}
    
    \vspace{-8pt}
\end{center}

\vspace{1pt}
\section{About Me}

I am a machine learning engineer with experience building real-world AI solutions to solve complex business problems. 
My expertise spans deep learning and computer vision, with a focus on medical imaging analysis. 
I am passionate about leveraging AI to create value and positive impact. 
I have a proven ability to understand business needs and deliver robust AI technologies that meet them. 
I am a collaborative team player and lifelong learner, continuously expanding my skills in this fast-evolving field. 
I am excited to continue growing as an ML Engineer, taking abstract concepts and turning them into practical innovations that augment human capabilities.


\section{Work Experiences}
\resumeSubHeadingListStart
\resumeSubheadingD
{Machine Learning Engineer }{Jun 2023 – Present}
{Mofid Securities }{}
{ 
	In my role, I transformed AI concepts into practical products. For instance:
}
\resumeItemListStart
\resumeItem{Built a conversational AI assistant with OpenAI's GPT-3 API to provide personalized financial guidance to customers, improving satisfaction scores by 15%}
\resumeItem{Implemented speech recognition to automatically transcribe videos into text summaries, extracting key details}
\resumeItem{Served some Open-source projects in production such as PyAnnote Diarization and Whisper for local usage}
\resumeItem{Using Prompt Engineering approaches to use LLMs such as OpenAI and Claude effectively}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Deep Learning Researcher }{Jan 2021 – Jun 2023}
{Data Science and Machine Learning Lab, Sharif University of Technology }{Supervisor: Hamid R. Rabiee}
{ 
 }

\resumeItemListStart
\resumeItem{Real-time Automatic Polyp detection and classification using Interpretable AI (XAI):
The purpose of this work is to enhance the YOLO algorithm's performance in handling labeled and unlabeled data using a semi-supervised learning framework. The study proposes an innovative approach that integrates semi-supervised learning and interpretability to improve the performance and transparency of the YOLO algorithm. To achieve this, pseudo-labeling is employed for semi-supervised learning, and the PyTorch-GradCAM library is adapted to work with YOLOv5, making it interpretable. 
}
\resumeItem{Real-time Detection of Brain Aneurysms using Multi-View YOLOv5:
Our project involved customizing the YOLOv5 algorithm to detect brain aneurysms in 2.5D CT scans. The network structure was modified to accept multiple images of the same patient as a single input, which helped the network to make better use of available information.
}
\resumeItemListEnd 

\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheadingD
{Software Developer - Full-Stack Web Developer}{July 2016 – January 2020}
{Amapardazesh Sepand Inc. }{Supervisor: S. Tavakoli}
{ The projects I worked on during my four years with Sepand Inc. were as follows: }

\resumeItemListStart
\resumeItem{Query Optimization in SQL-Server}
\resumeItem{Automatic updating of application using GoogleDrive API}
\resumeItem{ Report generator for DataGridView in StimulSoft Report }
\resumeItem{Integrating different devices (POS, Scale, SMS, TelegramBot) with Sepand Application}
\resumeItem{Database Schema Comparer and Upgrader using DACPAC}
\resumeItemListEnd 
% todo, Talk about my web developer experiences. wpf. windows form. 
\resumeSubHeadingListEnd

\begin{comment}
\resumeSubHeadingListStart
\resumeSubheadingD
{English Teacher }{July 2017 – January 2018}
{Zaban Gostar Institute  }{Supervisor: F. Fatemi}
{ I served as an English teacher for pre-intermediate students for one semester
}
\resumeSubHeadingListEnd
\end{comment} 


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, 
	label={}
	]
	\small{\item{
			\textbf{Programming Languages}{: Proficient: Python, C\#, SQL (T-SQL); Intermediate: Java, MATLAB } \\
			\textbf{Data Science Libraries}: PyTorch, Pandas, Numpy, OpenCV, scikit-learn, Matplotlib, Scrapy \\
			\textbf{Developer Tools}{:  VS Code, Jupyter Notebooks , VIM, Visual Studio, Android Studio} \\
			%\textbf{Technologies/Frameworks}{: ASP.NET MVC, Jekyll } \\
			\textbf{Databases}{: Proficient in SQL-Server, Familiarity with Mongo-Db } \\
			\textbf{Tools}{: Git, Docker, Jekyll, Hugo, \LaTeX , } \\
			\textbf{Operating Systems}{: Manjaro  (Arch Linux), Kubuntu  (Debian), Fedora (KDE spin), Windows } \\
	}}
\end{itemize}
\vspace{-16pt}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Sep. 2020 - Present}
      {Master of Science in Artificial Intelligence and Robotics}{Tehran, Iran}
  \resumeSubHeadingListEnd
    

\begin{itemize}[itemsep=-3pt, parsep=5pt]
\item  GPA: 18.83/20

\item Relevant courses:
Deep Learning,
Natural Language Processing, Computer Vision,
Machine Learning 
\end{itemize}  


  \resumeSubHeadingListStart
    \resumeSubheading
      {Yazd University}{Sep. 2016 - Sep. 2020}
      {Bachelor of Science in Computer Engineering}{Yazd, Iran}
  \resumeSubHeadingListEnd
  
\begin{itemize}[itemsep=-3pt, parsep=5pt]
	\item  GPA: 17.47/20
	
	\item Relevant courses:
	Intelligent and Expert Systems, Algorithms and Data Structures, Principles of Database Design, Foundations of Information Retrieval and Web Search
\end{itemize}  

  
\begin{comment}
\resumeSubHeadingListStart
    \resumeSubheading
      {Malek Sabet High School}{Sep 2012 - June. 2016}
      {Diploma in Physics and Mathematics Discipline}{Yazd, Iran}
  \resumeSubHeadingListEnd
 \small{ GPA: \textbf{19.49}/20, Units: 102, {\href{https://en.wikipedia.org/wiki/Governmental_leading_high_school}{ Affiliation: Governmental leading high school}}
\end{comment}  


\section{Internships}

\resumeSubHeadingListStart
\resumeSubheadingD
{Web Application and RESTful API for Restaurant}{July 2018 – October 2018}
{Amapardazesh Sepand Inc. }{Supervisor: S. Tavakoli}
{
	As well as developing a RESTful API service for Android devices, I built a dashboard  (based on ASP.NET) for managers to customize the restaurant according to their preferences.
}
\resumeSubHeadingListEnd

\section{Industrial Projects}

%todo sort by time
\resumeSubHeadingListStart
\resumeSubheadingD
{Heart Rate Monitor Application (ECG)}{
	July 2019 - Sep 2019
}
{Yazd University}
{Supervisor: Prof. V. Derhami}
{The app receives real-time data from a wireless ECG device via Bluetooth and displays it as a graph. However, some of the data was distorted or lost, making it difficult to consistently display it. }
\resumeSubHeadingListEnd


\resumeSubHeadingListStart
\resumeSubheadingD
{Web application to manage invoice and account }{January 2019 – March 2019}
{Amapardazesh Sepand Inc., Tavoni Etebar Kargaran Bafgh (Samen)}{Supervisor: S. Tavakoli}
{
	This web application provides a RESTful API for Android clients and an ASP.NET web application to show customers how much they owe the company.}
\resumeSubHeadingListEnd




\resumeSubHeadingListStart
\resumeSubheadingD
{Car Management for IranKhodro}{July 2013 – November 2013}
{Amapardazesh Sepand Inc., IranKhodro Yazd (4022 Branch - Farashahi)}{Supervisor: S. Tavakoli}
{ My first encounter with any programming language was with this Windows-forms application that managed parking lots, controlled vehicle entrance and exit, and generated management reports. }
\resumeSubHeadingListEnd

% todo: Add ML (help afhsin)
% todo: ADD SML
% todo: add Image processing
% todo : add AI-Project in derhami class

\section{Open Source Contributions}
\resumeSubHeadingListStart
\resumeSubheading
{Maintainer of al-folio Jekyll Theme}{June 2022}
{Link to repo: \url{https://github.com/alshedivat/al-folio} }{Owner: Al-Shedivat}{
	
}
\resumeSubHeadingListEnd



\resumeSubHeadingListStart
\resumeSubheading
{Contributions to YOLOv5}{2022}
{Link to repo: \url{https://github.com/ultralytics/yolov5},
	\href{https://github.com/ultralytics/yolov5/issues/9059}{\#9059},
	\href{https://github.com/ultralytics/yolov5/pull/8694}{\#8694},
	\href{https://github.com/ultralytics/yolov5/pull/8766}{\#8766}  
}{Maintainer: Glenn Jocher}{ 
	%	I have solved a very important bug and I have some PRs
}
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Open source Crawler for Persian websites}{July 2022}
{Link to repo: \url{https://github.com/pourmand1376/PersianCrawler} }{Maintainer: Me}
\resumeSubHeadingListEnd

\end{document}




\begin{comment}
list of things in my linkedin which are deleted

Update Sepand with google drive
Google Drive Api for upgrading appliction
work with google drive API's to upgrade existing application files such as DLL's, reports and so on.  This was replacement for Microsoft Click Once Deployment customized for our business.
The app is written with c# in a WPF application.

!this one has github link! 
Telegram bot for group manangement
Using telegram bot documentation from api.telegram.org, I've written a bot for managing groups in telegram. It can detect URL's, turn the group off at night, filter messages, delete inapropriate content and etc.

Comparing and Updating SQL Server database
I've written an application for updating customer local SQL Server databases through Sqlpackage which uses DAC framework.
This way we can compare two databases and generate script for updating schema in about 2 minutes. It also works with google drive api to download .dacpac file.

Report generator for Stimulsoft report
\end{comment}


\begin{comment}
\resumeSubHeadingListStart
\resumeSubheading
{Integrating different devices and technologies with Sepand software }{July 2016 – January 2020}
{Amapardazesh Sepand Inc.}{Supervisor: S. Tavakoli}

\resumeItemListStart
\resumeItem{Scale: Radin, MahakScale, Sadr, TarazSystem, Azma}
\resumeItem{POS: IranKish, SamanKish, IranKish, TejaratPardakht, MabnaKartArya}
\resumeItem{SMS: NegarSMS, Tooba, SMSNiaz}
\resumeItem{CallerId: ManshooreSimin}
\resumeItem{TelegramBots: Manager Reports Bot, Group Manager Bot}
\resumeItem{GoogleDrive: Updating sepand accounting software with files hosted on google drive automatically}
\resumeItemListEnd 
\resumeSubHeadingListEnd  
%todo this should be included in sepand desc



\resumeSubHeadingListStart
\resumeSubheadingD
{Database Schema Comparer and Upgrader}{April 2019 – May  2019}
{Amapardazesh Sepand Inc.}{Supervisor: S. Tavakoli}
{ Compare two SQL-server databases and update the schema of the database to newer version }
\resumeSubHeadingListEnd

\end{comment}
